03 Data Vizualization

### 2022-05-24 03_data_viz.Rmd
removed timecourse option

# BacDive Data
bacdive_FA <- readRDS(file = "cache/bacdive_FA")
bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide.RDS")

@@

# Define a function for turnover plots
plot_turnover <- function(df, terrain_choice, color_choice) {
  df %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    time_course == "0d -->",
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  mutate(type = "unweighted") %>% 
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%

@@

turnover_summarized %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    time_course == "0d -->",
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%

>>>>

# BacDive Data
bacdive_FA <- readRDS(file = "cache/bacdive_FA.RDS")
bacdive_FA_wide <- readRDS(file = "cache/bacdive_FA_wide.RDS")

@@

# Define a function for turnover plots
plot_turnover <- function(df, terrain_choice, color_choice) {
  df %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  mutate(type = "unweighted") %>% 
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%

@@

turnover_summarized %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%
